\documentclass[a4paper]{simplecv}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{url}

\usepackage[margin=1.2in,footskip=0.25in]{geometry}

\begin{document}

\leftheader{+595 961 47 19 47\\
\texttt{garyservin@gmail.com}}

\rightheader{
\texttt{Date of bith: October 12th, 1988}\\
\texttt{Nationality: Paraguayan}\\
\texttt{San Carlos 956, Asunción, Paraguay}}

\title{Gary Stephen Servín Cardozo}

\maketitle

\section{Summary}

I'm an electronics engineer working on different areas related to Robotics and programming. I love building robots, contributing to open source projects and sharing knowledge. \\

\begin{itemize}
\item \url{https://www.openhub.net/accounts/garyservin}
\item \url{https://github.com/garyservin}
\end{itemize}

\section{Education}

\begin{topic}

\item[2007 - 2013] {\bf Bachelor of Science (B.Sc.), Electronics Engineering, Emphasis Mechatronics} - National University of Asunción, Asunción, Paraguay.

{\bf Thesis:} \emph{Mobile Robotic Platform based on the inverted pendulum principle}.

%Advisor: Prof. Miki Saito.

\end{topic}

\section{Professional Experience}

\begin{topic}

    \item[February 2014 - Present] \emph{Software Engineer - Robotics} - Ekumen (\url{http://www.ekumenlabs.com}): Software development company.

        \begin{itemize}

            \item Software Testing Infrastrucure for Continuous Integration of Autonomy Software

            \item Development of autonomous multirotor navigation software using ROS.

            \item Porting ROS to Android devices.

        \end{itemize}

    \item[March 2014 - July 2014] \emph{Graduated Teaching Assistant} - Electricity and Electronics Department, Polytechnic Faculty - National University of Asunción.

    \item [April 2012 - January 2014] \emph{Software Engineer} - Engineering and IP Services Department, Copaco S.A. (\url{http://www.copaco.com.py}): Internet Service Provider.

    \item[September 2011 - July 2013] \emph{Teaching Assistant} Engineering Faculty - National University of Asunción.

\end{topic}

\section{Open source contributions and talks}

\begin{topic}

    \item[November 2013 - Present] \emph{Creator, Hardware Engineer} - Robot Didáctico Inalámbrico (RoDI).

        \url{http://rodibot.com/}

    \item[June 2016] \emph{Expositor} - Pyday 2016 Caacupe.

        Talk: Educational Robotics with RoDI

        \url{http://pyday.ctscaacupe.com/}

    \item[October 2015] \emph{Expositor} - ROSCon 2015 Hamburg.

        Talk: ROS Android NDK, What? Why? How?

        \url{http://www.osrfoundation.org/gary-servin-ekumen-ros-android_ndk-what-why-how/}

    \item[July 2015] \emph{Expositor, organizer} - Robotics PY 2015.

        Talk: Robot Operating System

    \item[April 2015] \emph{Expositor} - Robotics day.

        Talk: Robótica y Educación

        \url{http://www.roboticsday.org/speaker/gary-servin/}

    \item[March 2015] \emph{Expositor} - Pyday 2015 Asuncion.

        Talk: Robots \& Python

        \url{http://pyday.pythonpy.org/}

    \item[October 2014 - Present] \emph{Contributor} - Robot Operating System

        Maintainer of the ROS Serial Mbed and the ROS Android NDK packages.

        \url{http://wiki.ros.org/rosserial_mbed}

    \item[November 2013 - January 2014] \emph{Mentor} - Sugar Lab.

        Mentor for the Google Code In Competition.

        \url{http://wiki.sugarlabs.org/go/Google_Code_In_2013}

    \item[September 2012 - Present] \emph{Coordinator} - Robotics Club FPUNA.

        In charge of the coordination of activities of the Robotics Club of the Polythecnic Faculty of the National University of Asunción.

\end{topic}

\section{Publications in Journals and Conferences}

\begin{thebibliography}{10}

\footnotesize

\bibitem{servin11}
G. Servín, L. Sandoval. \emph{Prototipo de un Transportador Personal con Sistema de Balance Automático}, $^{XIX}$ Jornadas de Jóvenes Investigadores Asociación de Universidades del Grupo Montevideo, Oct 25-27, 2011, Paraguay. ISBN:978-99967-637-0-0

\bibitem{servin2012a}
Cardozo, G.S.S. and Vera, L.M.S. . \emph{Creation of a robotics club in the Universidad Nacional de Asunción based on the experience of horizontal learning in the University of Buenos Aires}. Engineering Applications (WEA), 2012 Workshop on. May, 2012, Bogotá, Colombia. ISBN:978-1-4673-0871-7

\bibitem{servin2012b}
Cardozo, G.S.S. and Vera, L.M.S. . \emph{Prototype for a Self-Balanced Personal Transporter}. Engineering Applications (WEA), 2012 Workshop on. May, 2012, Bogotá, Colombia. ISBN:978-1-4673-0871-7

\bibitem{servin2013}
Gary Servín, Luis Sandoval. \emph{Plataforma robótica móvil para prácticas basada en el principio del péndulo invertido}. $4^{th}$ Workshop of Robotics in Education (WRE 2013). October, 2013, Arequipa, Peru. ISBN:978-85-7669-284-3

\end{thebibliography}

%\section{References:}

%\begin{itemize}

%\item Phd. Emilio Luque, Professor, PhD advisor, Universitat Autonoma de Barcelona, Phone/Fax:(+595-21) 371-222. Email: emilio.luque@uab.es.

%\item Phd. Benjamín Barán, Professor, PhD program director, Polytechnic Faculty, National University of Asunción, Phone/Fax:(+595-21) 371-222. Email: bbaran@cnc.una.py.

%\item Phd. Luca Cernuzzi, Dean, Science and Technology Faculty, Catholic University "Nuestra Señora de la Asunción" . Phone: (+595-21) 334.650. Fax: (+595-21) 310-072. Email: lcernuzz@uca.edu.py.

%\end{itemize}

%\section{Additional Information}

%I am an Engineer very passionated about computer science and technology, self-motivated and hard-worker. I love to design and develop computer programs, solve hard problems and learn new algorithms, techniques and tools.

\end{document}
